What We Eval in the Shadows

### 2021-08-11 paper/main.tex
revert \c to \code

\begin{table}[!b]\small
\begin{tabular}{crrrrrc}\toprule
  \bf $min(e)$& \bf \#sites & \bf \%sites & \bf \#packages & \bf \#operations & \bf \%envir & \bf example\\\midrule
\code X&\packageMinimizedcallsitesa &\packageMinimizedpropsitesa &\packageMinimizedpackagea &\packageMinimizedmedianoperationsaRnd &\packageMinimizedpercentparentframesa & \code{y+1}\\
\code{F(F(X))} & \packageMinimizedcallsitesb  & \packageMinimizedpropsitesb & \packageMinimizedpackageb  & \packageMinimizedmedianoperationsbRnd & \packageMinimizedpercentparentframesb & \code{gbov( mean(x), a-1)}\\
\code{V}&\packageMinimizedcallsitesc &\packageMinimizedpropsitesc &\packageMinimizedpackagec &\packageMinimizedmedianoperationscRnd &\packageMinimizedpercentparentframesc& \code{c(42,21,0)}\\
\code{F(X)}& \packageMinimizedcallsitesd & \packageMinimizedpropsitesd & \packageMinimizedpackaged & \packageMinimizedmedianoperationsdRnd & \packageMinimizedpercentparentframesd & \code{seq\_len(iters)} \\
\code{$} & \packageMinimizedcallsitese & \packageMinimizedpropsitese & \packageMinimizedpackagee & \packageMinimizedmedianoperationseRnd & \packageMinimizedpercentparentframese & \code{DF\$B}\\
\code{model.frame}& \packageMinimizedcallsitesf & \packageMinimizedpropsitesf & \packageMinimizedpackagef & \packageMinimizedmedianoperationsfRnd & \packageMinimizedpercentparentframesf &  \code{model.frame(formula = Z ~  U)}   \\
\code{F()}& \packageMinimizedcallsitesg & \packageMinimizedpropsitesg & \packageMinimizedpackageg & \packageMinimizedmedianoperationsgRnd & \packageMinimizedpercentparentframesg & \code{rgamma(3, 2, n = 10L)} \\
\code{FUN} & \packageMinimizedcallsitesh & \packageMinimizedpropsitesh & \packageMinimizedpackageh & \packageMinimizedmedianoperationshRnd & \packageMinimizedpercentparentframesh & \code{function(x, y) x + 3 * y} \\
\code{<-} & \packageMinimizedcallsitesi  & \packageMinimizedpropsitesi & \packageMinimizedpackagei & \packageMinimizedmedianoperationsiRnd & \packageMinimizedpercentparentframesi & \code{x[1, 2:3, 2:3] <- value}\\
\code{BLOCK} & \packageMinimizedcallsitesj & \packageMinimizedpropsitesj & \packageMinimizedpackagej & \packageMinimizedmedianoperationsjRnd & \packageMinimizedpercentparentframesj & \code{{ write.csv(iris, tf) ; file.size(tf) }} \\\bottomrule
\end{tabular}
\caption{Minimized expressions} \label{tab:minimizedexpressions}
\end{table}

The expressions passed to \eval vary widely. We categorize expressions using a
minimization function which abstract some of the incidental details of
expressions and return a ``shape'' that can be used to group similar \evals. The
function $min(e)$ which for a given expression $e$ returns a normal form. Normal
forms use \c V to stand in for values occurring in expression, \c X stands in
for variables, and \c F stands for functions. The function performs constant
folding of arithmetic and string expressions over base operators, for instance
$min(\c{1+1})$ simplifies to \code{V}, on the ground that addition of values
likely returns a value. Value simplification takes $min$(\code{c(1,2,3+2)}) to
\code{V} as a complex vector containing values is a value. Variable absorption
has $min$(\code{x+y}) becomes \code{X}, this motivated by the fact that addition is
not an ``interesting'' operation, and that \code{X} stands in for any number of
variable lookups. Function absorption simplifies nested functions to keep an
abstraction of the nesting $min$(\code{g(f(x),h(z))})$=$\code{F(F(X))}. There are other
simplifications, the full list can be found in our artifact. It is worth
mentioning that these simplifications are heuristics, in R \code{1+1} is not
necessary \code{2}. The addition operator can be redefined, but it typically isn't
or at least not in a way that would invalidate arithmetic.

@@

\begin{tabular}{@{}p{.97\linewidth}}
  \vspace{1mm}
  \EE{$min(e)=\code{V}$} \\[-2mm]\small Values occur in 16\% of sites, 74\% of
  those are constants such as integers, the remainder evaluate to a value. \Eval
  is needed when the expression denoting the values is constructed
  programmatically. Cases when a value is directly given to \eval, and \eval
  returns it unchanged, often occur when a computation has a default path and
  another, more interesting, path that requires evaluation. The following is a
  call site that always see a string; \packageNbCallSitesUniqueActualValue of
  sites only ever see a value. This shape usually run in few interpreter steps.
  The environment in which they evaluate is mostly irrelevant.
\begin{lstlisting}
  eval(paste("A~",paste(paste(names(X[,-1])),collapse="+")))
\end{lstlisting}
\vspace{2mm}
\EE{$min(e)=\code{X}$}\\[-2mm]\small Variable lookups are the most common shape,
\packageNbSymbolVarSitePercent are simple variable names, e.g. \c x. The shapes
subsumes \c{V} and built-in arithmetic operations, so a mixture of arithmetics
and variables normalize to \c X. A lookup is one step of execution, if a promise
is returned an arbitrary number of additional steps may be needed; the median is
\packageMinimizedmedianoperationsaRnd, suggesting that most variable read do
little work. Variables are often evaluated in environments that have been
constructed programmatically, \packageMinimizedpercentparentframesa of
expressions are evaluated in a function environment.
\vspace{2mm}
\EE{$min(e)=\code{\$}$}\\[-2mm]\small This shape extends \c X to include lookup
with the dollar operator, \eg~\c{x\$f}, and vector indexing, \eg~\c{x[42]} and
\c{x[[24]]}. This takes a few more step of evaluation on average, and is
typically used in a function environment.

\vspace{2mm}
\EE{$min(e)=$~\code{<-}}\\[-2mm]\small This includes both direct
assignment {\tt <-} and parent environment assignment {\tt <\,\!<-} as well as
the \c{assign} function. It subsumes \c{\$}. Assignments represent the most
obvious source of side effects in \eval. Most cases originate from trivial code
generation where the assign expression is assembled using parse or substitute,
often in a loop. For example (taken from \c{PopED::get\_rse}), the following
code will populate the current scope with a number of variables:
%
\begin{lstlisting}
for (i in seq_along(args)) eval(parse(text=paste(args[i], "<-", i)))
\end{lstlisting}

\vspace{2mm}
\EE{$min(e)=\code{F()}$}\\[-2mm]\small Function calls without variable lookups or
assignment. A variable is allowed the function position, looking up
functions does not trigger computation unless the function's name
is bound to a promise. This shape typically does not perform much work.
\vspace{2mm}
\framebox{$min(e)=\code{F(X)}$}~\EE{$min(e)=\code{F(F(X))}$}\\[-2mm]\small Function
calls whose arguments may include variable references and nested calls. Together
they represent the most frequent shape and perform over 16 steps. They are
frequently evaluated in function environments.
\end{tabular}

\begin{tabular}{@{}p{.97\linewidth}}
  \medskip\EE{$min(e)=$ \code{FUN}}\\[-2mm]\small Function definitions without any
  computation, \eg~\c{function(x) x+1}. In addition to \c{FUN},
  \packageGeneralizedFunctionDefinitionSitesPercent of sites have function
  definitions nested in other expressions.

\vspace{2mm}
\EE{$min(e)=\code{BLOCK}$}\\[-2mm]\small Multi-statement code blocks, as
they can be large we do not try to normalize their contents. They execute in a
median \packageMinimizedmedianoperationsjRnd steps, usually, in function
environments.

\vspace{2mm}
\EE{$min(e)=\code{model.frame}$}\\[-2mm]\small The \c{model.frame} function
returns a dataframe resulting from fitting the model described in a formula.
This shape subsumes \c{F(F(X))}, \c{FUN}, and assignments. It is the single most
popular function invoked from \eval. Each call does a median of 2K instructions.
\end{tabular}

\paragraph{Discussion.} The number of different shapes that any given
\eval site sees is an indication of the versatility of that site.
\packageNbOneMinimizedPercent of sites only see a single expression shape. It
would be encouraging if one could, given a small training set, predict the shape
of \evals to come. In our corpus, only a few sites are highly polymorphic with
more than eight shapes. An example of those is the pipe operator of the
\c{magrittr} package which is used to compose functions, \eg instead of
\code{f(g(h(x),y),z)} one can write \code{h(x) \%>\% g(y) \%>\% f(z)}. As there many
different patterns of use, there are also many different shapes. In comparison
with R, JavaScript's \eval usage was more straightforward and more predictable
as reported by \citet{oopsla12b}, with 98\% of sites with only one shape. On the
other hand, there are \packageNbSimpleMinimizedOne sites that only receive one
of the simple shape (\ie\xspace \code{X}, \code{V}, \code{\$} or \code{<-}), and
\packageNbSimpleMinimizedMore sites get multiple simple shapes. Among these
sites, there are many cases where \eval could be replaced by simpler constructs
such as \code{get} to lookup a name in an environment, \code{assign} to set a value to
a name in an environment, or \code{do.call} to call a function reflectively.

@@

\begin{itemize}[---]
\item \emph{Function:} environments for the local variables of some function
  currently active on the call stack. Obtained by calling \code{parent.frame()} or
  \code{sys.frame()}.
\item \emph{Synthetic:} environments built from data structures such as lists,
  data.frames, or constructed explicitly with \code{new.env}, \code{list2env}, or
  \code{as.environment} or the empty environment.
\item \emph{Global:} environments in which scripts or interactive commands are
  evaluated.
\item \emph{Package:} environments of libraries.
\end{itemize}

@@

Each synthetic environment has parent that is specified when calling
\code{new.env}. When \code{envir} is a list or a data frame, \eval uses its third
argument (\code{enclos}). The parent is used to search for variables not found in
its child (side-effects stay in the child). Table~\ref{tab:newenvs} shows parent
kinds for synthetic environments. Most of them are functions.

Global \evals split between intentional and accidental one. Direct references to
the top-level, using \code{globalenv()} or \code{.GlobalEnv}, are rare; they occur in
only \packageNbExplicitGlobalSites sites. Thus we suspect most uses of global
are accidental. They arise from the fact that our corpus, consists of many code
snippet that are run at top-level, global is thus the caller of \eval. This
noteworthy because writes to global variables are visible to all functions and
are not reclaimed by the garbage collector. So accidental uses may pollute that
namespace. Table~\ref{tab:polyenvir} gives the number of kinds seen at a given
call site.

@@

One bit of information that we lack is how the environment was obtained. Our
expectation is that the expression was extracted from a promise using
\code{substitute}, perhaps modified, and then evaluated with the environment coming
from the same promise. We believe the case where \eval is provided the results
of programmatically selecting some call stack to be less frequent.

@@

Where does the expression passed to \eval come from? There are various means of
creating an expression, often these means correlate with a particular use case.
Our analysis records the values returned by some functions of interest as well
as their arguments. We build a direct acyclic graph that track the provenance of
the values that are given to \eval. The following example yields the provenance
graph with five nodes on Figure~\ref{fig:provgraph} for expression \code{e}.

@@

The provenance of \code{e} includes both \code{parse} and \code{quote}. We pick an origin
by traversing the graph from the root, following the left-hand side member of
assignments until a leaf. It represents the provenance that is further modified
to yield the expression passed to \eval. In our example, the origin is \code{parse}.

@@

Table~\ref{tab:provenance} summarizes provenance. Some sites are invoked with
different provenances, they are counted multiple times. Strings correlate with
dynamic code loading as done by \code{source} and \code{sys.source}. Few calls
(\packageNbParseFromFileSites in total) consume the result of calling \code{parse}
on a file. Most build strings programmatically. We identified one function
\code{invokeRestartInteractively} that prompts the user for input and \evals it.

\paragraph{Discussion}
The main use case for \eval involves using \code{match.call}, \code{substitute}, or
\code{formals} to access and transform arguments of a function. Constructing
expressions from strings is also a common use case. The constructed category
shows that most \evals comes from existing code that was modified by the
programmer before invoking \eval. Both constructed and reflection categories
roughly correspond to meta-programming. Some use cases could likely be replaced
by macros if the R designers could be convinced to overcome their distaste for
those. Another use of \eval is to directly build symbols to evaluate them in
another environment.

@@

The use of \eval with \code{substitute} is a general pattern that we often see
in R packages. It is used to make the interfaces more flexible. For example the
\c{subset}, which selects columns in a data frame, uses it to allow to specify
the selected columns using either the column name or index. For example
\c{subset(df, sel=c(1,B,x))} returns a subset of \code{df} with the first
column, the column named \code{B} and whatever column is at index the variable
\code{x} holds.

It is implemented using \code{eval(substitute(sel), nl, parent.frame())}. The
first argument returns the expression passed to \code{sel}. The second is a
named list that contains the names of the columns from \code{df} and which will
be used to evaluate the expression. The last parameter indicates which
environment should be used to look up bindings not found in \c{nl}.

>>>>

\begin{table}[!b]\small
\begin{tabular}{crrrrrc}\toprule
  \bf $min(e)$& \bf \#sites & \bf \%sites & \bf \#packages & \bf \#operations & \bf \%envir & \bf example\\\midrule
\c X&\packageMinimizedcallsitesa &\packageMinimizedpropsitesa &\packageMinimizedpackagea &\packageMinimizedmedianoperationsaRnd &\packageMinimizedpercentparentframesa & \c{y+1}\\
\c{F(F(X))} & \packageMinimizedcallsitesb  & \packageMinimizedpropsitesb & \packageMinimizedpackageb  & \packageMinimizedmedianoperationsbRnd & \packageMinimizedpercentparentframesb & \c{gbov( mean(x), a-1)}\\
\c{V}&\packageMinimizedcallsitesc &\packageMinimizedpropsitesc &\packageMinimizedpackagec &\packageMinimizedmedianoperationscRnd &\packageMinimizedpercentparentframesc& \c{c(42,21,0)}\\
\c{F(X)}& \packageMinimizedcallsitesd & \packageMinimizedpropsitesd & \packageMinimizedpackaged & \packageMinimizedmedianoperationsdRnd & \packageMinimizedpercentparentframesd & \c{seq\_len(iters)} \\
\c{\$} & \packageMinimizedcallsitese & \packageMinimizedpropsitese & \packageMinimizedpackagee & \packageMinimizedmedianoperationseRnd & \packageMinimizedpercentparentframese & \c{DF\$B}\\
\c{model.frame}& \packageMinimizedcallsitesf & \packageMinimizedpropsitesf & \packageMinimizedpackagef & \packageMinimizedmedianoperationsfRnd & \packageMinimizedpercentparentframesf &  \c{model.frame(formula = Z $\sim$ U)}   \\
\c{F()}& \packageMinimizedcallsitesg & \packageMinimizedpropsitesg & \packageMinimizedpackageg & \packageMinimizedmedianoperationsgRnd & \packageMinimizedpercentparentframesg & \c{rgamma(3, 2, n = 10L)} \\
\c{FUN} & \packageMinimizedcallsitesh & \packageMinimizedpropsitesh & \packageMinimizedpackageh & \packageMinimizedmedianoperationshRnd & \packageMinimizedpercentparentframesh & \c{function(x, y) x + 3 * y} \\
\c{<-} & \packageMinimizedcallsitesi  & \packageMinimizedpropsitesi & \packageMinimizedpackagei & \packageMinimizedmedianoperationsiRnd & \packageMinimizedpercentparentframesi & \c{x[1, 2:3, 2:3] <- value}\\
\c{BLOCK} & \packageMinimizedcallsitesj & \packageMinimizedpropsitesj & \packageMinimizedpackagej & \packageMinimizedmedianoperationsjRnd & \packageMinimizedpercentparentframesj & \c{\{ write.csv(iris, tf) ; file.size(tf) \}} \\\bottomrule
\end{tabular}
\caption{Minimized expressions} \label{tab:minimizedexpressions}
\end{table}

The expressions passed to \eval vary widely. We categorize expressions using a
minimization function which abstract some of the incidental details of
expressions and return a ``shape'' that can be used to group similar \evals. The
function $min(e)$ which for a given expression $e$ returns a normal form. Normal
forms use \c V to stand in for values occurring in expression, \c X stands in
for variables, and \c F stands for functions. The function performs constant
folding of arithmetic and string expressions over base operators, for instance
$min(\c{1+1})$ simplifies to $\c{V}$, on the ground that addition of values
likely returns a value. Value simplification takes $min(\c{c(1,2,3+2)})$ to
$\c{V}$ as a complex vector containing values is a value. Variable absorption
has $min(\c{x+y})$ becomes $\c{X}$, this motivated by the fact that addition is
not an ``interesting'' operation, and that \c X stands in for any number of
variable lookups. Function absorption simplifies nested functions to keep an
abstraction of the nesting $min(\c{g(f(x),h(z))})=\c{F(F(X))}$. There are other
simplifications, the full list can be found in our artifact. It is worth
mentioning that these simplifications are heuristics, in R \c{1+1} is not
necessary \c 2. The addition operator can be redefined, but it typically isn't
or at least not in a way that would invalidate arithmetic.

@@

\begin{tabular}{@{}p{.97\linewidth}}
  \medskip\EE{$min(e)=\c{V}$} \\[-2mm]\small Values occur in 16\% of sites, 74\% of
  those are constants such as integers, the remainder evaluate to a value. \Eval
  is needed when the expression denoting the values is constructed
  programmatically. Cases when a value is directly given to \eval, and \eval
  returns it unchanged, often occur when a computation has a default path and
  another, more interesting, path that requires evaluation. The following is a
  call site that always see a string; \packageNbCallSitesUniqueActualValue of
  sites only ever see a value. This shape usually run in few interpreter steps.
  The environment in which they evaluate is mostly irrelevant.
\begin{lstlisting}
  eval(paste("A~",paste(paste(names(X[,-1])),collapse="+")))
\end{lstlisting}
\\
\medskip\EE{$min(e)=\c{X}$}\\[-2mm]\small Variable lookups are the most common shape,
\packageNbSymbolVarSitePercent are simple variable names, e.g. \c x. The shapes
subsumes \c{V} and built-in arithmetic operations, so a mixture of arithmetics
and variables normalize to \c X. A lookup is one step of execution, if a promise
is returned an arbitrary number of additional steps may be needed; the median is
\packageMinimizedmedianoperationsaRnd, suggesting that most variable read do
little work. Variables are often evaluated in environments that have been
constructed programmatically, \packageMinimizedpercentparentframesa of
expressions are evaluated in a function environment.
\\
\medskip\EE{$min(e)=\c{\$}$}\\[-2mm]\small This shape extends \c X to include lookup
with the dollar operator, \eg~\c{x\$f}, and vector indexing, \eg~\c{x[42]} and
\c{x[[24]]}. This takes a few more step of evaluation on average, and is
typically used in a function environment.
\\
\medskip\EE{$min(e)=$~\c{<-}}\\[-2mm]\small This includes both direct assignment {\tt
  <-} and parent environment assignment {\tt <\,\!<-} as well as the \c{assign}
function. It subsumes \c{\$}. Assignments
represent the most obvious source of side effects in \eval.
\\
\medskip\EE{$min(e)=\c{F()}$}\\[-2mm]\small Function calls without variable lookups or
assignment. A variable is allowed the function position, looking up
functions does not trigger computation unless the function's name
is bound to a promise. This shape typically does not perform much work.
\\
\medskip\framebox{$min(e)=\c{F(X)}$}~\EE{$min(e)=\c{F(F(X))}$}\\[-2mm]\small Function
calls whose arguments may include variable references and nested calls. Together
they represent the most frequent shape and perform over 16 steps. They are
frequently evaluated in function environments.
\end{tabular}

\begin{tabular}{@{}p{.97\linewidth}}
  \medskip\EE{$min(e)=\c{FUN}$}\\[-2mm]\small Function definitions without any
  computation, \eg~\c{function(x) x+1}. In addition to \c{FUN},
  \packageGeneralizedFunctionDefinitionSitesPercent of sites have function
  definitions nested in other expressions.
\\
\medskip\EE{$min(e)=\c{BLOCK}$}\\[-2mm]\small Multi-statement code blocks, as
they can be large we do not try to normalize their contents. They execute in a
median \packageMinimizedmedianoperationsjRnd steps, usually, in function
environments.
\\
\medskip\EE{$min(e)=\c{model.frame}$}\\[-2mm]\small The \c{model.frame} function
returns a dataframe resulting from fitting the model described in a formula.
This shape subsumes \c{F(F(X))}, \c{FUN}, and assignments. It is the single most
popular function invoked from \eval. Each call does a median of 2K instructions.
\end{tabular}

\paragraph{Discussion.} The number of different shapes that any given
\eval site sees is an indication of the versatility of that site.
\packageNbOneMinimizedPercent of sites only see a single expression shape. It
would be encouraging if one could, given a small training set, predict the shape
of \evals to come. In our corpus, only a few sites are highly polymorphic with
more than eight shapes. An example of those is the pipe operator of the
\c{magrittr} package which is used to compose functions, \eg instead of
\c{f(g(h(x),y),z)} one can write \c{h(x) \%>\% g(y) \%>\% f(z)}. As there many
different patterns of use, there are also many different shapes. In comparison
with R, JavaScript's \eval usage was more straightforward and more predictable
as reported by \citet{oopsla12b}, with 98\% of sites with only one shape. On the
other hand, there are \packageNbSimpleMinimizedOne sites that only receive one
of the simple shape (\ie\xspace \c{X}, \c{V}, \c{\$} or \c{<-}), and
\packageNbSimpleMinimizedMore sites get multiple simple shapes. Among these
sites, there are many cases where \eval could be replaced by simpler constructs
such as \c{get} to lookup a name in an environment, \c{assign} to set a value to
a name in an environment, or \c{do.call} to call a function reflectively.

@@

\begin{itemize}[---]
\item \emph{Function:} environments for the local variables of some function
  currently active on the call stack. Obtained by calling \c{parent.frame()} or
  \c{sys.frame()}.
\item \emph{Synthetic:} environments built from data structures such as lists,
  data.frames, or constructed explicitly with \c{new.env}, \c{list2env}, or
  \c{as.environment} or the empty environment.
\item \emph{Global:} environments in which scripts or interactive commands are
  evaluated.
\item \emph{Package:} environments of libraries.
\end{itemize}

@@

Each synthetic environment has parent that is specified when calling
\c{new.env}. When \c{envir} is a list or a data frame, \eval uses its third
argument (\c{enclos}). The parent is used to search for variables not found in
its child (side-effects stay in the child). Table~\ref{tab:newenvs} shows parent
kinds for synthetic environments. Most of them are functions.

Global \evals split between intentional and accidental one. Direct references to
the top-level, using \c{globalenv()} or \c{.GlobalEnv}, are rare; they occur in
only \packageNbExplicitGlobalSites sites. Thus we suspect most uses of global
are accidental. They arise from the fact that our corpus, consists of many code
snippet that are run at top-level, global is thus the caller of \eval. This
noteworthy because writes to global variables are visible to all functions and
are not reclaimed by the garbage collector. So accidental uses may pollute that
namespace. Table~\ref{tab:polyenvir} gives the number of kinds seen at a given
call site.

@@

One bit of information that we lack is how the environment was obtained. Our
expectation is that the expression was extracted from a promise using
\c{substitute}, perhaps modified, and then evaluated with the environment coming
from the same promise. We believe the case where \eval is provided the results
of programmatically selecting some call stack to be less frequent.

@@

Where does the expression passed to \eval come from? There are various means of
creating an expression, often these means correlate with a particular use case.
Our analysis records the values returned by some functions of interest as well
as their arguments. We build a direct acyclic graph that track the provenance of
the values that are given to \eval. The following example yields the provenance
graph with five nodes on Figure~\ref{fig:provgraph} for expression \c{e}.

@@

The provenance of \c{e} includes both \c{parse} and \c{quote}. We pick an origin
by traversing the graph from the root, following the left-hand side member of
assignments until a leaf. It represents the provenance that is further modified
to yield the expression passed to \eval. In our example, the origin is \c{parse}.

@@

Table~\ref{tab:provenance} summarizes provenance. Some sites are invoked with
different provenances, they are counted multiple times. Strings correlate with
dynamic code loading as done by \c{source} and \c{sys.source}. Few calls
(\packageNbParseFromFileSites in total) consume the result of calling \c{parse}
on a file. Most build strings programmatically. We identified one function
\c{invokeRestartInteractively} that prompts the user for input and \evals it.

\paragraph{Discussion}
The main use case for \eval involves using \c{match.call}, \c{substitute}, or
\c{formals} to access and transform arguments of a function. Constructing
expressions from strings is also a common use case. The constructed category
shows that most \evals comes from existing code that was modified by the
programmer before invoking \eval. Both constructed and reflection categories
roughly correspond to meta-programming. Some use cases could likely be replaced
by macros if the R designers could be convinced to overcome their distaste for
those. Another use of \eval is to directly build symbols to evaluate them in
another environment.

@@
